workshop

### 2022-09-13 scripts/workshop.Rmd
tb_pca version of fig 2

>>>>

tb_pca_scores_summ %>% ggplot(.,aes(x=pc1Rank, y=cc)) + geom_point(aes(color = Month, shape = factor(WetAltID), size = size))+
  labs(x="Principal Component 1", y = "Community Competence (CC)", size = "Host\nAbundance") + 
  scale_shape_manual(values = rep(1:20, len = 20)) +
  scale_size_continuous(range = c(2,10)) +
  guides(shape=F) +
  theme_classic() +
  theme(aspect.ratio=1/1.618, legend.box = "horizontal") +
  scale_color_viridis_d(direction = -1) +
  theme(text = element_text(size=18))
